Palomar 5 Gaps

### 2024-10-22 paper/main.tex
starting gap creation rate calculation

      Lastly, \citet{2012ApJ...748...20C} conceptualized the number of gaps with a statistical quantity, the rate at which gaps are created per unit stream-length. To put our results in these terms, the global cluster population has a gap creation rate on Palomar 5 of XXX.

>>>>

      Lastly, \citet{2012ApJ...748...20C} conceptualized the number of gaps with a statistical quantity, the rate at which gaps are created per unit stream-length. For our simulations, this is given by:\begin{equation}
      \mathcal{R}_{\textrm{Pal 5}} =  \frac{1}{T}\int_{0}^T l^{-1}(t) \sum_i \delta(t-t_i) dt,\end{equation}where $T$ is the total integration time, $l(t)$ is the length of the stream, and $\sum_i \delta(t-t_i)$ sums over the number of gap occurances, where the index $i$ iterates over the number of gaps in a given simulation since $\delta$ is the diract delta function. This can be simplified to:\begin{equation}\mathcal{R}_{\textrm{Pal 5}} =  \frac{1}{T} \sum_i \frac{1}{l (t_i)}. \end{equation}
